### 2021-02-25 paper/fse21/implementation.tex
Marked inred.

\paragraph{Synchronization of Control Points.}
For seamless interaction between static analysis and {\sealed} execution,
synchronization of control points in both sides is necessary.
The SAFE and Jalangi have their own notations for control points that are not directly
compatible.
We use the source-code location of a target program as a key to synchronize.
Even though they use different parsers and we faced numerous location mismatches for corner cases,
we could synchronize control points of two analyzers by using the closest match
of their source-code locations rather than using exact match of them.

>>>>

\paragraph{Synchronization of Control Points.}
For seamless interaction between static analysis and {\sealed} execution,
synchronization of control points in both sides is necessary.
\inred{The SAFE and Jalangi have their own notations for control points that are not directly
compatible.
We use the source-code location of a target program as a key to synchronize.
Even though they use different parsers and we faced numerous location mismatches for corner cases,
we could synchronize control points of two analyzers by using the closest match
of their source-code locations rather than using exact match of them.}
